---
title: "Creating a Leaflet Map"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.align='center', message = FALSE, warning=FALSE)
```


### Submission by Connor Lenio. Email: cojamalo@gmail.com

## Completion Date: Jun 19, 2017

## Goal

Create a web page using R Markdown that features a map created with Leaflet. My map will show the major gyms near my home with their address and links to the gym's websites.

## Load packages

```{r}
library(leaflet)
library(htmltools)
library(dplyr)
```

## Creating a custom icon

The following code creates two different custom icons for use in the leaflet call:
```{r}
strongIcon <- makeIcon(
  iconUrl = "https://s3.amazonaws.com/cojamalo/misc/leafleticon1.png",
  iconWidth = 60, iconHeight = 70,
  iconAnchorX = 0, iconAnchorY = 0
)
homeIcon <- makeIcon(
  iconUrl = "https://s3.amazonaws.com/cojamalo/misc/houseiconleaflet.png",
  iconWidth = 60, iconHeight = 60,
  iconAnchorX = 0, iconAnchorY = 0
)
```

## Prepare marker data

The following vectors supply the input data for the markers in the leaflet call:
```{r}
loc_lng = c(-77.067280, -77.052347, -77.103329, -77.054084, -77.060069)
loc_lat = c(38.84600, 38.843133, 38.837406, 38.821083, 38.827681)

labels = c("Gold's Gym", "LA Fitness", "Xsport Fitness", "YMCA", "Mount Vernon Rec Center")

content <- c(paste(sep = "<br/>", "<b><a href='http://www.goldsgym.com/southarlingtonva/'>Gold's Gym</a></b>", "2955 S. Glebe Rd", "Arlington, VA 22206"),
            paste(sep = "<br/>", "<b><a href='https://www.lafitness.com/Pages/clubhome.aspx?clubid=542&ARLINGTON-Virginia+GYUM&utm_source=google&utm_medium=googlemaps&utm_campaign=maps'>LA Fitness</a></b>", "3550 S Clark St", "Arlington,  VA  22202"),
            paste(sep = "<br/>", "<b><a href='http://www.xsportfitness.com/locations/alexandria-va-gym.html'>Xsport Fitness</a></b>", "4300 King St", "Alexandria, VA 22302"),
            paste(sep = "<br/>", "<b><a href='http://www.ymcadc.org/branch.cfm?bid=02&utm_source=local&utm_medium=organic&utm_campaign=gmb'>YMCA</a></b>", "420 East Monroe Ave", "Alexandria, VA 22301"),
            paste(sep = "<br/>", "<b><a href='https://www.alexandriava.gov/recreation/info/default.aspx?id=95493'>Mount Vernon Rec Center</a></b>", "2701 Commonwealth Ave", "Alexandria, VA 22305")
             )
```



## Calling leaflet

Finally, leaflet is called to produce the final map:
```{r}
map = leaflet() %>% 
        addTiles() %>% 
        addProviderTiles(providers$Stamen) %>% # Custom styling for the map
        addMarkers(lng=-77.073528, lat=38.841367, popup = c("Home"), , icon = homeIcon) %>%
        addMarkers(lng=loc_lng, lat=loc_lat, popup = content, label = labels, icon = strongIcon, labelOptions= labelOptions(noHide = F))
map
```

* * *
